\documentclass[12pt,courier]{navyletter}


\usepackage{designature}

\author{Dennis Evangelista}
\title{Letter of recommendation for Ricardo Casas Roman}
\navysubj{Letter of recommendation for MIDN 2/C Ricardo Roman}
\navyfiling{}
\navyserial{}
\date{\today}
\navymarking{}

\begin{document}
\makedateblock{}

\begin{navyletterheader}
\navyfrom{Assistant Professor Dennis Jose Evangelista\newline Department of Weapons \& Systems Engineering}
\navyto{Admissions Board}
\navyskip{}%
\navysubjline{}%
%\navyskip{}%
%\navyref{refa}{CVN-71 letter Ser 1234, dtd 2 Jan 2016}
%\navyref{refb}{NAVSEA 250-1500-1 Nuclear Welding Manual}
%\navyref{refc}{Bettis letter Ser 5678, dtd 1 Feb 2016}
%\navyencl{encl1}{blah}
\end{navyletterheader}

\section{}
This letter of recommendation is on behalf of MIDN 2/c Ricardo Roman.  Mr.~Roman was a student in my Introduction to Mechatronics course, taught to all systems engineering majors during their second year here at the Academy. The course introduces mechatronics, combining basic electronics, mbed microcontrollers, basic control systems, and mechanical engineering design.  Mr.~Roman overcame early difficulties, and with hard work and determination he ultimately received a B in the class. 

\section{} 
Among his highly competetive group of fellow engineering midshipmen, MIDN 2/c Roman distinguished himself with strong, applied, hands-on, technical skills in electronics.  I am always happy to have prior enlisted veterans like Mr.~Roman, because of their strengths and real-world experiences.  When my course started circuits, I was able to rely on Mr.~Roman's assistance in helping his peers setup and debug lab exercises and project hardware.  In such tasks, he was a confident technican and debugger and a patient teacher. 

\section{}
I am sad to hear Mr.~Roman is transferring from the Academy, as I would have enjoyed working with him on a senior capstone project.  I am happy to recommend him as a transfer student to complete his engineering degree.  I am also happy to recommend him for other programs as he sees fit to use this letter.  I have taught veteran transfer students at UC Berkeley and I believe Mr.~Roman is of the same caliber. I have no doubt that regardless of his path, he will succeed at higher responsibilities in citizenship, government, engineering or industry.

\noclosing{}\\
\noindent\hspace*{4in}\includesignature{}
\signature{D EVANGELISTA}

%\copyto
%File
\end{document}